Introduction to Causal Inference Models

### 2017-07-19 msm_introduction.Rmd
my package failed to install.
need to change something in the msmodelr package.

>>>>

Standard regression estimate.

```{r time dependent std regression}
std_td_mod <- glm(Y~A0 + A1 + A0*A1, family = "gaussian", data = td_sim_data)

```

Now that we have our simulated data, we'll replicate the results Naimi et al.
of marginal (overall) effect of HIV treatment on CD4 count.

To make things easier, let's load some functions I've made for g-computation and IPTW.

```{r}
# install custom package MSModelR
# devtools::install_github("RyanGan/MSModelR")

# load library
library(MSModelR)
```
